\LARGE \bf Autonomous Object Manipulation using a Soft Planar Grasping Manipulator

### 2018-04-08 experimental_results.tex
blacn and white

\subsection{Experimental Platform}
The \dr{soft manipulation} system is shown in Figure~\ref{fig:experimental_platform}.
%The planar six segment soft rubber manipulator consists of twelve distributed elastomer actuators. This manipulator moves with minimal friction on a level plane.
%A soft rubber gripper is fixed to the tip of the manipulator.
Each arm segment is 6.27\unit{cm} and the soft gripper is 10.6\unit{cm} long.
The localization system OptiTrack Flex 3 by Natural Point provides real-time measurements of marked points both along the inextensible back of the manipulator and on top of the object. 
A rigid frame holds all the subsystems \rkk{as a mobile presentation platform} together providing reliable hardware experiments without the need for recalibration.

\begin{figure}[htbp]
\begin{centering}
  \includegraphics[width=2.0in]{Figures/system_overview/sys_overview_smaller}\\
  \caption{System Overview. The system is composed of (\textbf{A}) a motion capture system, (\textbf{B}) rigid frame, (\textbf{C}) soft six segment planar manipulator, (\textbf{D}) an object within the grasp envelope, (\textbf{E}) a soft gripper fixed to the manipulator, (\textbf{F}) a fluidic drive cylinder array to control actuation, and (\textbf{F}) computers for real-time processing and control.} \label{fig:experimental_platform}
\end{centering}
\end{figure}

@@

\begin{figure}[htb]
\centering
   \includegraphics[width=0.8\columnwidth]{Figures/experimental_results/uncertainty}
   \caption{Experimental characterization of the gripper's capture region: the allowable positioning uncertainty is determined through repeated placements of the center of a cylindrical object at different points on a grid relative to the gripper. Blue dots indicate all object center positions for which a grasp could be performed successfully, red crosses show the positions where a grasp failed. The grey line outlines an area for the object to be positioned within so the gripper can grasp it. The evaluation of the capture region was performed similarly to a method described in \cite{dogar2010push}.}
   \label{fig:grasp_uncertainty}
\end{figure}

\subsection{Grasp Experiments}
\rkk{Using the experimental platform in Figure~\ref{fig:experimental_platform}, we implemented the planning algorithm described in Section~\ref{sec:processing_and_control}.
We evaluated the manipulator system for repeatability and ability to handle uncertainty.
The experiments consisted of picking and placing several objects of unknown geometry placed at an unknown location.
We measured the execution time and captured the location data during the experiments.
Specifically,}
we performed over 200 experimental grasp-and-place trials at various positions to demonstrate the capabilities and repeatability of our system.
We picked up various objects such as eggs, shuttlecocks, bakery items, cups, light bulbs, and tape holders. 
The objects had an enclosing diameter in the range of 2-5\unit{cm}. 
The results of a subset of those experimental trials are shown in Figure~\ref{fig:allTestsOverlaid}.
One representative approach, grasp, and retract move is shown in Figure~\ref{fig:oneTrialVsTime}.
In 23 of 25 experimental trials shown, the manipulator successfully achieved the task of grasping an object and placing it at a bin location shown in red.
\rkk{The test object has a weight of 18\unit{g} and a diameter of 3.3\unit{cm}.}
The object was placed five times on each of the five points marked on the board.
The markers only serve as a reference point for the user to place the object roughly at the same point at every repetition.
The user's placing accuracy is not important to the algorithm, \rkk{since the tracking system newly registers the position of the object every time it is placed.}
The five points were chosen to approximately represent the major portion of the manipulator's reachable workspace.
As long as the root of the gripper stops so that the object is located within the capture region, the gripper will pick it up through its sweeping closing motion. The capture region is shown in grey in Figure~\ref{fig:grasp_uncertainty}.

The evaluation of the capture region is performed similarly to a method described in Dogar and Srinivasa\cite{dogar2010push} work on determining capture regions for a push-grasp of a classical robotic gripper.
\rkk{Grid paper and fine markings on all four sides of the round object ensure that the placement by the user is accurate within $\pm$1\unit{mm} in relation to the discrete placement locations on the grid. This test serves as a qualitative measure to show qualitatively a relation between object size to gripper size to area of successful grasp.}
\rkk{This characterization was repeated two times, resulting always in the same capture region.}
Despite positioning inaccuracies of the soft manipulator, the gripper can nevertheless successfully perform a grasp of an object.

When the arm reaches \rkk{its straight pose within a relatively large delta}, it drops the object.
\rkk{For these experiments, we focus on showing the capability of picking up objects at various places and moving them around, there is no emphasis set on having to drop off the object at a specific pose. To indicate that the arm can move the object after grasping, the arm was controlled to go back to the fully straight pose. When it got fairly close to that final straight pose within a large allowable delta, the gripper was set to release and drop the object. It was not ensured by the planner that the arm had to first settle to zero velocity at the final straight pose. As a consequence of this, the experimental data indicates as a red bin a relatively wide drop off area.}

\begin{figure*}[htbp]
\begin{centering}
  \includegraphics[width=0.5\textwidth]{Figures/experimental_results/allTestsOverlaid.eps}
\includegraphics[width=0.385\textwidth]{figures/experimental_results/five_grasps.jpg}
\caption[Left: All 25 experimental grasping trials.]{Complete set of experimental grasp-and-place trials. In these experiments, the arm moves from an initial straightened configuration to grasp a round object placed in one of five locations (A-E). The arm then returns the object to a bin location shown in red. For each trial, a seven degrees of freedom manipulator representation is generated at both the \emph{grasped} and \emph{released} state using experimental data and is shown in blue. The corresponding 1 degree-of-freedom end-effector representation is shown in black. The round object's measured position at each state is shown in green. Right: Overlaid photographs of the manipulator grasping an object placed at each of the five locations. }\label{fig:allTestsOverlaid}
\end{centering}
\end{figure*}

The unsuccessful trials happened due to stick-slip friction between the roller bearings and the table surface.
Our kinematic modeling does not account for this non-linear behavior, which acts as a disturbance and can lead to failure to arrive at the next waypoint.
%To be more specific, in one of the trials, the robot slowed down too much before it almost reached its next waypoint and because of friction the arm halted to a full stop. 
%The proportional gain of the curvature controller was not able to compensate for that small positional delta and since the relatively low saturation level of the integrator portion of the controller was saturated, the arm did not move to the next waypoint pose. 
%It is to note, that the saturation level for the integrator is defined by a safety limit on the maximal inflation of the robotic arm.
%In the other unsuccessful trial, the stick-slip friction also caused the arm to halt before a waypoint. The controller built up enough forcing due to inflation, so that the arm slipped over the close waypoint without having all of its single arm segment curvature within an acceptable epsilon.
%The controller then tried to swing back to fulfill the missed waypoint, missed it again and that finally caused the whole arm to oscillate back-and-forth and eventually push the object off the table.
In one of the trials shown in Figure~\ref{fig:allTestsOverlaid}, the grasp and return was successfully performed, but an overshoot over the final bin location caused the arm to drop off the relatively small table.
%, which could have been avoided if the table would have not been too small towards the right.
%This outlier is shown in Figure~\ref{fig:allTestsOverlaid}.

@@

\rkk{We developed an end-to-end system that can approximately locate an object placed at an a priori unknown location and move it somewhere else. The external localization system is a convenient way to approximately identify the location of the object and to track how the object is moved around.
The exteroceptive tracking system has the disadvantage that the full occlusion of one or more markers can cause the tracking system to temporarily loose track of a measured arm segment. 
In that case, the control loop can not function properly until the occlusion disappears. 
The external localization system could be replaced with another method for localizing the manipulator and the object in the workspace.
For example, proprioceptive sensors within the segments could solve this issue partially. 
A first step towards proprioceptive sensing was done for three soft fingers arranged as a hand in \cite{homberg2015haptic}.}

\begin{figure*}[htbp]
\begin{centering}
  \includegraphics[width=0.375\textwidth]{Figures/experimental_results/oneTrialVsTime.eps}
\includegraphics[width=0.30\textwidth]{figures/experimental_results/exp5a-4_sweep_to_object.jpg}
\includegraphics[width=0.31\textwidth]{figures/experimental_results/exp5a-4_sweep_to_bin.jpg}
  \caption{Left: A time series representation of an experimental grasp-and-place trial for an object located at point E. Here, the locally optimal planned manipulator configurations as well as planned sequential approach circles are shown as black dotted curves. The arm and gripper are shown in their experimentally determined configuration representations at 1 second intervals. The cyan configurations represent the manipulator prior to grasping the object, that is moving from its initial configuration to the object's location. \rkk{Depending on where the object is placed, the arm takes between 17-35\unit{s} to approach it.} The magenta configurations represent the manipulator after grasping the object, that is moving from the object's location back to the bin location shown in red. \rkk{This task of moving back to the bin takes between 10-20\unit{s}.} Right: A photograph of the arm moving from its initial pose to the object and from the object to the release location, respectively.}
\label{fig:oneTrialVsTime}
\end{centering}
\end{figure*}

\rkk{The experiments were performed for picking up objects on the left quadrant of the manipulator.
Grasping objects on both sides of the manipulator could be achieved in various ways by 
\begin{enumerate}
\item replacing the large gripper at the end of the arm with two smaller grippers next to each other, 
\item mounting roller supports on the top face of the manipulator and then rotating the manipulator at its root by $180^{\circ}$,
\item increasing the reachable workspace through starting the soft arm at an extreme curvature configuration within the right quadrant.  
\end{enumerate}
}

>>>>

\subsection{Experimental Platform}
The \dr{soft manipulation} system we developed for this work is shown in Figure~\ref{fig:experimental_platform}.
%The planar six segment soft rubber manipulator consists of twelve distributed elastomer actuators. This manipulator moves with minimal friction on a level plane.
%A soft rubber gripper is fixed to the tip of the manipulator.
Each arm segment is 6.27\unit{cm} and the soft gripper is 10.6\unit{cm} long.
The localization system OptiTrack Flex 3 by Natural Point provides real-time measurements of marked points both along the inextensible back of the manipulator and on top of the object. 
A rigid frame holds all the subsystems \rkk{as a mobile presentation platform} together providing reliable hardware experiments without the need for recalibration.

\begin{figure}[htbp]
\begin{centering}
  \includegraphics[width=2.0in]{Figures/system_overview/sys_overview_smaller_bw.jpg}\\
  \caption{System Overview. The system is composed of (\textbf{A}) a motion capture system, (\textbf{B}) rigid frame, (\textbf{C}) soft six segment planar manipulator, (\textbf{D}) an object within the grasp envelope, (\textbf{E}) a soft gripper fixed to the manipulator, (\textbf{F}) a fluidic drive cylinder array to control actuation, and (\textbf{G}) computers for real-time processing and control.} \label{fig:experimental_platform}
\end{centering}
\end{figure}

@@

\begin{figure}[htb]
\centering
   \includegraphics[width=0.8\columnwidth]{Figures/experimental_results/uncertainty_bw}
   \caption{Experimental characterization of the gripper's capture region: the allowable positioning uncertainty is determined through repeated placements of the center of a cylindrical object at different points on a 5\unit{mm} grid relative to the gripper. Blue dots indicate all object center positions for which a grasp could be performed successfully, red crosses show the positions where a grasp failed. The grey line outlines an area for the object to be positioned within so the gripper can grasp it. The evaluation of the capture region was performed similarly to a method described in \cite{dogar2010push}.}
   \label{fig:grasp_uncertainty}
\end{figure}

\subsection{Grasp Experiments}
\rkk{Using the experimental platform in Figure~\ref{fig:experimental_platform}, we implemented the planning algorithm described in Section~\ref{sec:processing_and_control}.
We evaluated the manipulator system for repeatability and ability to handle uncertainty.
The experiments consisted of picking and placing several objects of unknown geometry placed at an unknown location.
We measured the execution time and captured the location data during the experiments.
Specifically,}
we performed over 200 experimental grasp-and-place trials at randomly chosen positions within the reachable workspace to demonstrate the capabilities and repeatability of our system.
We successfully picked up various objects such as eggs, shuttlecocks, bakery items, cups, light bulbs, and tape holders. 
The objects had an enclosing diameter in the range of 2-5\unit{cm}. 
The results of a subset of those experimental trials are shown in Figure~\ref{fig:allTestsOverlaid}.
One representative approach, grasp, and retract move is shown in Figure~\ref{fig:oneTrialVsTime}.
In 23 of 25 experimental trials shown, the manipulator successfully achieved the task of grasping an object and placing it at a bin location shown in red.
\rkk{The test object has a weight of 18\unit{g} and a diameter of 3.3\unit{cm}.}
The object was placed five times on each of the five points marked on the board.
The markers only serve as a reference point for the user to place the object roughly at the same point at every repetition.
The user's placing accuracy is not important to the algorithm, \rkk{since the tracking system re-registers the position of the object every time it is placed.}
The five points were chosen to approximately represent the major portion of the manipulator's reachable workspace.
As long as the root of the gripper stops so that the object is located within the capture region, the gripper will pick it up through its sweeping closing motion. The capture region is outlined in grey in Figure~\ref{fig:grasp_uncertainty}.

The evaluation of the capture region is performed similarly to a method described in Dogar and Srinivasa\cite{dogar2010push} work on determining capture regions for a push-grasp of a classical robotic gripper.
\rkk{Grid paper and fine markings on all four sides of the round object ensure that the placement by the user is accurate within $\pm$1\unit{mm} in relation to the discrete placement locations on the grid. This test serves as a qualitative measure to show qualitatively a relation between object size to gripper size to area of successful grasp.}
\rkk{This characterization was repeated two times, resulting in nearly identical capture regions.}
Despite positioning inaccuracies of the soft manipulator, the gripper can nevertheless successfully perform a grasp of an object. 
\rkk{The successful capture region can be characterized by about half a gripper length in diameter.}

When the arm reaches \rkk{its straight pose within a relatively large delta}, it drops the object.
\rkk{For these experiments, we focus on showing the capability of picking up objects at various places and moving them around, there is no emphasis set on having to drop off the object at a specific place. To indicate that the arm can move the object after grasping, the arm was controlled to go back to the fully straight pose. When the arm reached the final straight pose within a 1\unit{cm} delta, the gripper was set to release and drop the object. It was not ensured by the planner that the arm had to first settle to zero velocity at the final straight pose. As a consequence of this, the experimental data indicates as a red bin a relatively wide drop off area.}

\begin{figure*}[htbp]
\begin{centering}
  \includegraphics[width=0.5\textwidth]{Figures/experimental_results/allTestsOverlaid.eps}
\includegraphics[width=0.385\textwidth]{figures/experimental_results/five_grasps.jpg}
\caption[Left: All 25 experimental grasping trials.]{Left: Complete set of experimental grasp-and-place trials. In these experiments, the arm moves from an initial straightened configuration to grasp a round object placed in one of five locations (A-E). The arm then returns the object to a bin location shown in red. For each trial, a seven degrees of freedom manipulator representation is generated at both the \emph{grasped} and \emph{released} state using experimental data and is shown in blue. The corresponding 1 DOF end-effector representation is shown in black. The round object's measured position at each state is shown in green. In one of the trials, the grasp and return was successfully performed, but an overshoot over the final bin location caused the gripper to drop off the small table it is moving on. Right: Overlaid photographs of the manipulator grasping an object placed at each of the five locations. }\label{fig:allTestsOverlaid}
\end{centering}
\end{figure*}

The unsuccessful trials happened due to stick-slip friction between the roller bearings and the table surface.
Our kinematic modeling does not account for this non-linear behavior, which acts as a disturbance and can lead to failure to arrive at the next waypoint.
%To be more specific, in one of the trials, the robot slowed down too much before it almost reached its next waypoint and because of friction the arm halted to a full stop. 
%The proportional gain of the curvature controller was not able to compensate for that small positional delta and since the relatively low saturation level of the integrator portion of the controller was saturated, the arm did not move to the next waypoint pose. 
%It is to note, that the saturation level for the integrator is defined by a safety limit on the maximal inflation of the robotic arm.
%In the other unsuccessful trial, the stick-slip friction also caused the arm to halt before a waypoint. The controller built up enough forcing due to inflation, so that the arm slipped over the close waypoint without having all of its single arm segment curvature within an acceptable epsilon.
%The controller then tried to swing back to fulfill the missed waypoint, missed it again and that finally caused the whole arm to oscillate back-and-forth and eventually push the object off the table.
%, which could have been avoided if the table would have not been too small towards the right.
%This outlier is shown in Figure~\ref{fig:allTestsOverlaid}.

@@

\rkk{We developed an end-to-end system that can approximately locate an object placed at an a priori unknown location and move it to a desired location. The external localization system is a convenient way to approximately identify the location of the object and to track how the object is moved around.
The exteroceptive tracking system has the disadvantage that the full occlusion of one or more markers can cause the tracking system to temporarily loose track of a measured arm segment. 
In that case, the control loop can not function properly until the occlusion disappears. 
The external localization system could be replaced with another method for localizing the manipulator and the object in the workspace.
For example, proprioceptive sensors within the segments could solve this issue partially. 
A first step towards proprioceptive sensing was done for three soft fingers arranged as a hand in \cite{homberg2015haptic}.}

\begin{figure*}[htbp]
\begin{centering}
  \includegraphics[width=0.375\textwidth]{Figures/experimental_results/oneTrialVsTime.eps}
\includegraphics[width=0.30\textwidth]{figures/experimental_results/exp5a-4_sweep_to_object.jpg}
\includegraphics[width=0.31\textwidth]{figures/experimental_results/exp5a-4_sweep_to_bin.jpg}
  \caption{Left: A time series representation of an experimental grasp-and-place trial for an object located at point E (Figure~\ref{fig:allTestsOverlaid}). Here, the locally optimal planned manipulator configurations as well as planned sequential approach circles are shown as black dotted curves. The arm and gripper are shown in their experimentally determined configuration representations at 1 second intervals. The cyan configurations represent the manipulator prior to grasping the object, that is moving from its initial configuration to the object's location. \rkk{Depending on where the object is placed, the manipulator takes between 17-35\unit{s} to approach it.} After grasping the object, the magenta configurations represent the manipulator moving from the object's location back to the bin location shown in red. \rkk{This task of moving back to the bin takes between 10-20\unit{s}.} Right: Overlaid photographs of the manipulator moving from its initial pose to the object and from the object to the release location, respectively.}
\label{fig:oneTrialVsTime}
\end{centering}
\end{figure*}

\rkk{The experiments were performed for picking up objects on the left quadrant of the manipulator.
Grasping objects on both sides of the manipulator could be achieved in various ways including 
\begin{enumerate}
\item replacing the large gripper at the end of the arm with two smaller grippers next to each other, 
\item mounting roller supports on the top face of the manipulator and then rotating the manipulator at its root by $180^{\circ}$,
\item increasing the reachable workspace through starting the soft arm at an extreme curvature configuration within the right quadrant.  
\end{enumerate}
}

### 2018-04-08 robotic_gripper.tex
blacn and white

\section{Soft Grasping Manipulator}
\label{sec:soft_grasping_manipulator}
\rkk{The robotic manipulator is composed of multiple bidirectional planar arm segments and combined with a unidirectional soft gripper.}
%We first introduce the previously developed uniform channel design, which is used for the soft body arm segments.
%Following this, 
We briefly describe the design, fabrication and functionality of this soft grasping manipulator. Further details on the design and fabrication can be found in \cite{marchese2015recipe}.

@@

\begin{figure}[thpb]
\centering
   \includegraphics[width=0.99\columnwidth]{figures/robotic_gripper/design_gripper.eps}
   \caption{The pleated channel designs. (\textbf{A}) depicts the segment in an unactuated state and (\textbf{B}) shows the segment in an actuated and therefore bent state. The expansion of the pressurized channels are schematically represented. \rkk{Reproduced from \cite{marchese2015recipe}.}}
   \label{fig:design}
\end{figure}

@@

\subsection{Lost Wax Fabrication for Fluidic Elastomer Actuators}
Existing soft fluidic manipulators are mostly produced through a multi-step lamination process called soft lithography, which results in weakening seams that can easily delaminate. 
This limits their range of applications and lifetime.
\rkk{The retractable pin fabrication for uniform lateral channels, first introduced in \cite{marchese2014whole}, does not cause weakening seams to the actuator, but it also does not allow for cavities more complicated than cylindrical shapes.}
This is why the application of lost-wax casting to the fabrication of soft fluidic actuators like a gripper is advantageous.
The actuated cavities of the soft gripper are achieved by using a wax core, pourable silicone rubber and 3D printed molds.
The gripper fabrication process and the tools needed are fully described and depicted in Section~4.3. and Figure~14 of the recipes paper for soft fluidic elastomer actuators \cite{marchese2015recipe}. %Figure~\ref{fig:fabrication}.
%The tools and equipment used are also listed in Table~\ref{tab:MachineTools} and are referred to by superscripts.
%
%In step (A), harder silicone rubber$^6$ is poured into a mold, which contains a 3D-printed model of the wax core.
%In preparation for step (B), the model is removed and the rubber mold is left inside the outer mold.
%A rigid rod is \rkk{embedded} as a supportive inlay inside the wax core.
%The rod is laid into the cavity of the rubber mold, supported on both ends by the outer mold.
%This ensures that the wax core does not break when removed from the rubber mold.
%\rkk{Mold release spray is applied to the silicone rubber mold to ease the wax core removal process.}
%The bees-wax$^{7}$ is heated up until it becomes fully liquefied.
%The assembly of rubber mold and outer mold is then heated up for a few minutes to the same temperature as the wax.
%Using a syringe, the liquid wax is injected into the assembly.
%Within a few minutes, the injected wax will start to solidify and significantly shrink in volume; this is counteracted by injecting more hot wax into the solidifying wax core during cool down.
%In step (B), the wax core is first allowed to completely cool down, then it is released from the mold.
%In step (C), the cooled down wax core is assembled together with the bottom mold, which defines the pleated structure of the gripper.
%The mold assembly is aligned with a top mold using pins. This top mold provides for additional volume to cover the wax core.
%In step (D), low elastic modulus rubber$^1$ is mixed, degassed in a vacuum$^2$, and poured to form the gripper and allowed to cure.
%In step (E), stiffer rubber$^3$ is poured on top of the cured gripper to form a constraint layer.
%In step (F), the cured gripper is removed from the mold.
%In step (G), most of the wax core is melted out by placing the gripper into an oven in an upright position.
%After this, remaining wax residues are cooked out in a boiling water bath.
%Finally, in step (H) a silicone tube$^5$ and a piece of silicone cord$^{8}$ get covered with silicone sealant$^4$ and are inserted into the front and back holes respectively.
%
%\begin{table}[h]
%\caption{Commercially Available Tools and Equipment}
%\centering
%\begin{tabular}{c l l}
%\hline
%\hline
%\# & Product Name & Company\\
%\hline
%1 & Ecoflex 0030&  Smooth-On\\
%2 & AL Cube & Abbess Instr. and Sys., Inc.\\
%3 & Mold Star 15 & Smooth-On\\
%4 & Silicone Sealant 732 & Dow Corning Corp\\
%5 & PN 51845K53 & McMaster\\
%6 & Mold Star 30 & Smooth-On\\
%7 & Beeswax & Jacquard\\
%8 & PN 9808K21& McMaster\\
%\hline
%\end{tabular}
%\label{tab:MachineTools}
%\end{table}

@@

The design for the arm consisting of soft cylindrical segments was described in \cite{marchese2014whole}.
\rkk{As was shown in \cite{marchese2015recipe} through the characterization of various actuator morphologies, the concatenation of soft cylindrical segments is most suitable to build up a robotic arm that can create high blocking forces per fluid energy inserted.}
 \rkk{The cylindrical segments of the arm are fabricated through a retractable pin fabrication technique, which does not require lost wax cores because of their simple cylindrical cavities.} 
Each cylindrical segment can only be actuated up to a bend angle of about $60^\circ$, therefore several segments have to be combined together to allow the arm to reach a large enough workspace to perform proper manipulation tasks on a plane. 
\rkk{Using six segments, the joint limits do not prohibit the robot to reach with its tip its own root.} %Calculating the forward kinematics, see \texttt{forwKin()} in Algorithm~\ref{alg:planGrasp}, for the 6 DOF arm with a segment length of 6.27\unit{cm} and an extreme curvature of $\kappa = \frac{60/180 \pi}{0.0627\unit{m}} = 16.7\frac{1}{\unit{m}}$ shows that the tip of the robot can reach its root at a full curl.}
The cylindrical segment design with its hollow channel in the center has enough space to accommodate for pneumatic tubes to connect to all six cylindrical segments and additionally to the pleated gripper, which is attached to the tip. 
The pleated gripper has to be appropriately sized, just big enough to allow for proper manipulation without exceeding the payload capacity of the soft arm.

>>>>

\section{Soft Grasping Manipulator}
\label{sec:soft_grasping_manipulator}
\rkk{The robotic manipulator is composed of multiple bidirectional planar arm segments and combined with a unidirectional soft gripper.}
%We first introduce the previously developed uniform channel design, which is used for the soft body arm segments.
%Following this, 
We briefly describe the design, fabrication and functionality of this soft grasping manipulator in this paper. Further details on the design and fabrication can be found in \cite{marchese2015recipe}.

@@

\begin{figure}[thpb]
\centering
   \includegraphics[width=0.99\columnwidth]{figures/robotic_gripper/design_gripper_detailed_bw.eps}
   \caption{The pleated channel designs. The design consists of a channel inlet (a), an almost inextensible constraint layer (b), uniform pleats (d) separated by even gaps (c), and internal channels within each pleat (e). (\textbf{A}) depicts the segment in an unactuated state and (\textbf{B}) shows the segment in an actuated and therefore bent state. The expansion of the pressurized channels are schematically represented. \rkk{Reproduced from \cite{marchese2015recipe}.}}
   \label{fig:design}
\end{figure}

@@

\subsection{Lost Wax Fabrication for Fluidic Elastomer Actuators}
Existing soft fluidic manipulators are mostly produced through a multi-step lamination process called \emph{soft lithography}, which results in weakening seams that can easily delaminate. 
This limits their range of applications and lifetime.
\rkk{The retractable pin fabrication for uniform lateral channels, first introduced in \cite{marchese2014whole},
limits the complexity of the cavities to cylindrical shapes but does not cause weakening seams to the actuator.}
%does not cause weakening seams to the actuator, but it also does not allow for cavities more complicated than cylindrical shapes.}
This is why the application of lost-wax casting to the fabrication of soft fluidic actuators like a gripper is advantageous.
The actuated cavities of the soft gripper are achieved using a wax core, pourable silicone rubber and 3D printed molds.
The gripper fabrication process and the tools needed are fully described and depicted in Section~4.3. and Figure~14 in \cite{marchese2015recipe}. %Figure~\ref{fig:fabrication}.
%The tools and equipment used are also listed in Table~\ref{tab:MachineTools} and are referred to by superscripts.
%
%In step (A), harder silicone rubber$^6$ is poured into a mold, which contains a 3D-printed model of the wax core.
%In preparation for step (B), the model is removed and the rubber mold is left inside the outer mold.
%A rigid rod is \rkk{embedded} as a supportive inlay inside the wax core.
%The rod is laid into the cavity of the rubber mold, supported on both ends by the outer mold.
%This ensures that the wax core does not break when removed from the rubber mold.
%\rkk{Mold release spray is applied to the silicone rubber mold to ease the wax core removal process.}
%The bees-wax$^{7}$ is heated up until it becomes fully liquefied.
%The assembly of rubber mold and outer mold is then heated up for a few minutes to the same temperature as the wax.
%Using a syringe, the liquid wax is injected into the assembly.
%Within a few minutes, the injected wax will start to solidify and significantly shrink in volume; this is counteracted by injecting more hot wax into the solidifying wax core during cool down.
%In step (B), the wax core is first allowed to completely cool down, then it is released from the mold.
%In step (C), the cooled down wax core is assembled together with the bottom mold, which defines the pleated structure of the gripper.
%The mold assembly is aligned with a top mold using pins. This top mold provides for additional volume to cover the wax core.
%In step (D), low elastic modulus rubber$^1$ is mixed, degassed in a vacuum$^2$, and poured to form the gripper and allowed to cure.
%In step (E), stiffer rubber$^3$ is poured on top of the cured gripper to form a constraint layer.
%In step (F), the cured gripper is removed from the mold.
%In step (G), most of the wax core is melted out by placing the gripper into an oven in an upright position.
%After this, remaining wax residues are cooked out in a boiling water bath.
%Finally, in step (H) a silicone tube$^5$ and a piece of silicone cord$^{8}$ get covered with silicone sealant$^4$ and are inserted into the front and back holes respectively.
%
%\begin{table}[h]
%\caption{Commercially Available Tools and Equipment}
%\centering
%\begin{tabular}{c l l}
%\hline
%\hline
%\# & Product Name & Company\\
%\hline
%1 & Ecoflex 0030&  Smooth-On\\
%2 & AL Cube & Abbess Instr. and Sys., Inc.\\
%3 & Mold Star 15 & Smooth-On\\
%4 & Silicone Sealant 732 & Dow Corning Corp\\
%5 & PN 51845K53 & McMaster\\
%6 & Mold Star 30 & Smooth-On\\
%7 & Beeswax & Jacquard\\
%8 & PN 9808K21& McMaster\\
%\hline
%\end{tabular}
%\label{tab:MachineTools}
%\end{table}

@@

The design for the arm consisting of soft cylindrical segments is described in \cite{marchese2014whole}.
\rkk{As is shown in \cite{marchese2015recipe} through the characterization of various actuator morphologies, the concatenation of soft cylindrical segments is most suitable to build up a robotic arm that can create high blocking forces per fluid energy inserted.}
 \rkk{The cylindrical segments of the arm are fabricated through a retractable pin fabrication technique \cite{marchese2014whole}, which does not require lost wax cores because of their simple cylindrical cavities.} 
Each cylindrical segment can be actuated up to a bend angle of about $60^\circ$, this requires several segments to be combined together to allow the arm to reach a large enough workspace to perform proper manipulation tasks on a plane. 
\rkk{Using six segments, the robot is able to touch its tip to its base without interference from the individual joint limits.}
%the joint limits do not prohibit the robot to reach with its tip its own root.} %Calculating the forward kinematics, see \texttt{forwKin()} in Algorithm~\ref{alg:planGrasp}, for the 6 DOF arm with a segment length of 6.27\unit{cm} and an extreme curvature of $\kappa = \frac{60/180 \pi}{0.0627\unit{m}} = 16.7\frac{1}{\unit{m}}$ shows that the tip of the robot can reach its root at a full curl.}
The cylindrical segment design with its hollow channel in the center has enough space to accommodate for pneumatic tubes to connect to all six cylindrical segments and additionally to the pleated gripper, which is attached to the tip. 
The pleated gripper has to be appropriately sized, just big enough to allow for proper manipulation without exceeding the payload capacity of the soft arm.
